Measuring E-Mail Header Injections on the World Wide Web

### 2016-10-24 Background/php.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

\begin{lstlisting}[language=PHP,caption={PHP program with e-mail
      header injection vulnerability.},label={code:phpemi}, float]
$from = $_REQUEST['email'];
$subject = 'Hello XYZ';
$message = 'We need you to reset your password';
$to = 'xyz@xyz.edu';

// example attack string to be 
// injected as the value for
// $_REQUEST['email'] => 
// 's@s.com\nCC:spc@spc.com'
$retValue = mail($to, $subject, $message, "From: $from");
// E-Mail gets sent to both 
// xyz@xyz.edu AND spc@spc.com
\end{lstlisting}

>>>>

\begin{lstlisting}[language=PHP,caption={PHP program with e-mail
      header injection vulnerability.},label={code:phpemi}, float]
$from = $_REQUEST['email'];
$subject = 'Hello XYZ';
$message = 'We need you to reset your password';
$to = 'xyz@example.com';
$retValue = mail($to, $subject, $message, "From: $from");
\end{lstlisting}

### 2016-10-24 Background/py.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

\begin{lstlisting}[language=Python,caption={Python program with e-mail
      header injection vulnerability.},label={code:pyemi}, float]
from email.parser import Parser
import cgi
form = cgi.FieldStorage()
to = form["email"] # input() exhibits 
# the same behavior
msg = """To: """ + to + """\n
From: <user@example.com>\n
Subject: Test message\n\n
Body would go here\n"""

f = FeedParser() # Parser.parsestr() 
# also contains the same vulnerability
f.feed(msg)
headers = FeedParser.close(f)
# attack string => 
# 'abc@example.com\nBCC:spc@example.com'
# bcc:spc@example.com is added to headers
print 'To: %s' % headers['to']
print 'BCC: %s' % headers['bcc']
\end{lstlisting}

>>>>

\begin{lstlisting}[language=Python,caption={Python program with e-mail
      header injection vulnerability.},label={code:pyemi}, float]
from email.parser import Parser
import cgi
form = cgi.FieldStorage()
to = form["email"]
msg = """To: """ + to + """\n
From: <user@example.com>\n
Subject: Test message\n\n
Body would go here\n"""

f = FeedParser() 
f.feed(msg)
headers = FeedParser.close(f)
print 'To: %s' % headers['to']
print 'BCC: %s' % headers['bcc']
\end{lstlisting}

### 2016-10-24 Background/ruby.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

    This is a test e-mail message.
"""
# construct a post request with email set to attack_string
# attack_string => s@example.com%0abcc:spc@example.com%0aSubject:Hello
Net::SMTP.start('localhost',1025) do |smtp|
smtp.send_message message, 'sch@example.com', 'to@todomain.com'
end
# Headers get added, and Subject field changes to what we set.
end
\end{lstlisting}

>>>>

    This is a test e-mail message.
"""
Net::SMTP.start('localhost',1025) do |smtp|
smtp.send_message message, 'sch@example.com', 'to@todomain.com'
end
end
\end{lstlisting}

### 2016-10-24 Discussion/ethics.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

To make sure that our system did not cause any harm to the web applications that we crawled, we made sure that we did not inject any special characters other than the newline character% (characters that a developer would assume an average user could put in)
. We also had an information website at the IP that we crawled from\footnote{Removed for the sake of anonymity} that described what \ehi was, and contained our contact details in case the developers of the web applications we crawled wanted to contact us. We maintained a separate blacklist of domain names that the owners did not want us to crawl, and ensured that our system did not crawl their domains.

>>>>

To make sure that our system did not cause any harm to the web applications that we crawled, we made sure that we did not inject any special characters other than the newline character% (characters that a developer would assume an average user could put in)
. We also had an informational website at the IP that we crawled from that described what \ehi was, and contained our contact details in case the developers of the web applications we crawled wanted to contact us. We maintained a separate blacklist of domain names that the owners did not want us to crawl, and ensured that our system did not crawl their domains.

### 2016-10-24 Discussion/limits.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

		\begin{table}
			\centering
			\normalsize
			\begin{tabular}{|p{4cm}|c|c|}
				\hline
				\multicolumn{1}{|c}{\textbf{Method}} &
				\multicolumn{1}{|c|}{\textbf{Running time}} &
				\multicolumn{1}{|c|}{\textbf{Slowdown}}
				\\
				\hline
				\centering Using our pipeline & 629.043 & - \\
				\hline
				\centering Our pipeline with Selenium & 919.372 & \slowSelenium \\
				\hline				
				\centering Parsing \email fields instead of `grep'ing inside form & 707.154 & \slowParse \\								
				\hline
			\end{tabular}
			\caption[\titlecap{}]{Running times in seconds for crawling, parsing, and detecting presence of \email fields in 1000 random wikipedia pages.}
			\label{tab:perf}
		\end{table}

@@

		During the crawl, our system was blacklisted by a few web applications (mostly WordPress ones), and Internet Service Providers (ISPs).
		To overcome this, we did two things:
		\begin{enumerate}
			\item Used an IP range of 60 different IP addresses.
			\item Used a blacklist of our own to prevent our Fuzzer from fuzzing web application that are known to blacklist automated crawlers.  However, we could not gather any data about these web applications.
		\end{enumerate}

>>>>

		\begin{table}
			\centering
			\scriptsize
			\begin{tabular}{|p{4cm}|c|c|}
				\hline
				\multicolumn{1}{|c}{\textbf{Method}} &
				\multicolumn{1}{|c|}{\textbf{Running time}} &
				\multicolumn{1}{|c|}{\textbf{Slowdown}}
				\\
				\hline
				\centering Using our pipeline & 629.043 & - \\
				\hline
				\centering Our pipeline with Selenium & 919.372 & \slowSelenium \\
				\hline				
				\centering Parsing \email fields instead of `grep'ing inside form & 707.154 & \slowParse \\								
				\hline
			\end{tabular}
			\caption[\titlecap{}]{Running times in seconds for crawling, parsing, and detecting presence of \email fields in 1000 random wikipedia pages.}
			\label{tab:perf}
		\end{table}

@@

		During the crawl, our system was blacklisted by a few web
        applications (mostly WordPress ones), and Internet Service
        Providers (ISPs). To overcome this, we did two things: (1)
        used an IP range of 60 different IP addresses, and (2) Used a
        blacklist of our own to prevent our Fuzzer from fuzzing web
        application that are known to blacklist automated crawlers.
        However, we could not gather any data about these web
        applications.

### 2016-10-24 Discussion/mitigation.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

\subsection{Mitigation Strategy}
\label{disc:mitigation}
After demonstrating that \ehi vulnerabilities exist on the web at large, we now describe the most common measures that can be taken to prevent the occurrence of this vulnerability, or at least reduce the impact.
\begin{itemize}
	\item Use Mail Libraries\\
	Using a safe, well tested \email library is the preferred way of preventing \ehi vulnerabilities (removing the burden of input sanitization from the developer). 
	A list of known secure libraries for each language and framework discussed is shown in Table~\ref{tab:maillib}.

	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of \ehi vulnerability.
	\begin{table}[tbp]
		\centering
		\normalsize
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website:\\ https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
			\hline
			Python & SMTPLib with email.header.Header\tablefootnote{instead of using email.parser.Parser to parse the header}\\
			\hline
			Java & Apache Commons E-Mail\tablefootnote{Apache Commons E-Mail: https://commons.apache.org/proper/commons-email/}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\tablefootnote{Ruby Mail Website: https://rubygems.org/gems/mail}\\
			\hline
			WordPress & Contact Form 7\tablefootnote{Contact Form 7 Download: https://wordpress.org/plugins/contact-form-7/}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
		\label{tab:maillib}
	\end{table}
	\item Use a Content Management System (CMS) \\
	Content management systems such as WordPress and Drupal include libraries and plugins to prevent \ehi. Thus, websites built with such CMS' are usually resistant to these attacks. However, it is advised to use the correct \email plugin, as not all plugins might be secure.
	An example of a secure plug-in is included as part of Table~\ref{tab:maillib}.

	\item Input Validation\\
	If neither of the two options are feasible (website being an in-house production, or due to lack of support infrastructure), developers can choose to perform proper input sanitization. Sanitization should be done keeping in mind RFC5322~\cite{rfc5322}, and care must be taken to ensure that all edge cases are taken into account.

	%% Client Side validation alone is not sufficient, and must be supplemented by server-side validation to mitigate the attack. Constant updates to validation methods are required so that new attack vectors do not harm the website in any way.
	%% Test driven development for such validation methods is also encouraged so that we can be reasonably sure of our defense mechanisms.
\end{itemize}

>>>>

\subsection{Mitigation Strategy}
\label{disc:mitigation}
After demonstrating that \ehi vulnerabilities exist on the web at large, we now describe the most common measures that can be taken to prevent the occurrence of this vulnerability, or at least reduce the impact.

Using a safe, well tested \email library is the preferred way of
preventing \ehi vulnerabilities (removing the burden of input
sanitization from the developer). A list of known secure libraries for
each language and framework discussed is shown in
Table~\ref{tab:maillib}.

	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of \ehi vulnerability.
	\begin{table}[tbp]
		\centering
		\scriptsize
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website:\\ https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
			\hline
			Python & SMTPLib with email.header.Header\tablefootnote{instead of using email.parser.Parser to parse the header}\\
			\hline
			Java & Apache Commons E-Mail\tablefootnote{Apache Commons E-Mail: https://commons.apache.org/proper/commons-email/}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\tablefootnote{Ruby Mail Website: https://rubygems.org/gems/mail}\\
			\hline
			WordPress & Contact Form 7\tablefootnote{Contact Form 7 Download: https://wordpress.org/plugins/contact-form-7/}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
		\label{tab:maillib}
	\end{table}

Content management systems such as WordPress and Drupal include
libraries and plugins to prevent \ehi. Thus, websites built with such
CMS' are usually resistant to these attacks. However, it is advised to
use the correct \email plugin, as not all plugins might be secure. An
example of a secure plug-in is included as part of
Table~\ref{tab:maillib}.

If neither of the two options are feasible (website being an in-house
production, or due to lack of support infrastructure), developers can
choose to perform proper input sanitization. Sanitization should be
done keeping in mind RFC5322~\cite{rfc5322}, and care must be taken to
ensure that all edge cases are taken into account.

	%% Client Side validation alone is not sufficient, and must be supplemented by server-side validation to mitigate the attack. Constant updates to validation methods are required so that new attack vectors do not harm the website in any way.
	%% Test driven development for such validation methods is also encouraged so that we can be reasonably sure of our defense mechanisms.

### 2016-10-24 Results/analysis.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

\subsection{Analysis of the Received \Email Data}
During our analysis of the received \emails, we found that the \emails that we received belonged to three categories:
\begin{enumerate}
	\item \Emails with the \texttt{bcc} header successfully injected\\
	  This form of injection was our initial objective, and we found
% Adam: Sai, why isn't this number a command? - DONE.
      \ehibcc such \emails in our received \emails. This validates that the web applications that sent these \emails are vulnerable to \ehi.

	\item \Emails with the \texttt{to} header successfully injected\\
	We discovered an unintended vulnerability class during our analysis, which we call \texttt{To~header injection}. These injections reflect the ability to inject any number of \email addresses into the \texttt{to} field of the SMTP message while being unable to inject any other header into the \emails. We found \ehito such \emails in our received \emails. We attribute this behavior to inconsistent sanitization by the application. 
    % Adam: I can't understand what this sentence is trying to say - Removed.

@@

	\item \Emails with the \texttt{x-check} header successfully injected\\
    The third category of \emails received were \emails with the \texttt{x-check} header injected. As discussed in Section~\ref{analyze:detect_x_check}, 
    we can differentiate between unsuccessful attempts and successful attempts by injecting the additional header and checking whether headers other than the \texttt{bcc} header can be injected into the generated \email. \ehixcheck \emails were received with the \texttt{x-check} header injected.
\end{enumerate}

@@

\begin{itemize}
	\item \Email Header Injections with both \texttt{bcc} and \texttt{x-check} headers\\
	  These represent the scenario where an attacker can inject multiple headers into the \emails. We can see that 54\% of the received \texttt{bcc} header injected \emails are also susceptible to being injected with additional headers.
      % Adam: What is the exact percentage? We should use that rather than an approximate number - DONE.

	\item Both \texttt{To} header injections and \texttt{x-check} headers \\
	This combination shows us that in addition to being able to inject into the \texttt{To} fields, we injected additional headers into the \email. It is not clear what causes this behavior; however, these can be exploited to achieve the same result as a regular \ehi.

	\item Total \texttt{x-check} headers and unique \texttt{x-check} headers found in \texttt{nuser} \emails\\
		We found a total of \ehinuserxcheck \emails in the \texttt{nuser} account. Out of these, \ehiuniquenuserxcheck had unique form ids that were \emph{not} already found in the \texttt{maluser} account. We attribute these \emails to (probably) being sent by a web application that was built with Python or another language having a similar behavior with respect to ignoring duplicate headers while constructing an \email, thus appending the \texttt{x-check} header and \emph{not} the \texttt{bcc} header. 
      % Adam: What is the actual behavior? This is confusing. - Changed. DONE.

	\item Total successful injections\\
	  This represents the total number of successful injections. This includes the \ehi with \texttt{bcc} header\,(1), \texttt{To} header injections\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} \emails\,(7). A total of \success vulnerabilities were found by our system.

>>>>

\subsection{Analysis of the Received \Email Data}
During our analysis of the received \emails, we found that the \emails that we received belonged to three categories:

\Emails with the \texttt{bcc} header successfully injected. This form
of injection was our initial objective, and we found
% Adam: Sai, why isn't this number a command? - DONE.
\ehibcc such \emails in our received \emails. This validates that the
web applications that sent these \emails are vulnerable to \ehi.

\Emails with the \texttt{to} header successfully injected. We
discovered an unintended vulnerability class during our analysis,
which we call \texttt{To~header injection}. These injections reflect
the ability to inject any number of \email addresses into the
\texttt{to} field of the SMTP message while being unable to inject any
other header into the \emails. We found \ehito such \emails in our
received \emails. We attribute this behavior to inconsistent
sanitization by the application.
    % Adam: I can't understand what this sentence is trying to say - Removed.

@@

\Emails with the \texttt{x-check} header successfully injected. The
third category of \emails received were \emails with the
\texttt{x-check} header injected. As discussed in
Section~\ref{analyze:detect_x_check}, we can differentiate between
unsuccessful attempts and successful attempts by injecting the
additional header and checking whether headers other than the
\texttt{bcc} header can be injected into the generated \email.
\ehixcheck \emails were received with the \texttt{x-check} header
injected.

@@

\Email Header Injections with both \texttt{bcc} and \texttt{x-check}
headers. These represent the scenario where an attacker can inject
multiple headers into the \emails. We can see that 54\% of the
received \texttt{bcc} header injected \emails are also susceptible to
being injected with additional headers.
      % Adam: What is the exact percentage? We should use that rather than an approximate number - DONE.

Both \texttt{To} header injections and \texttt{x-check} headers. This
combination shows us that in addition to being able to inject into the
\texttt{To} fields, we injected additional headers into the \email. It
is not clear what causes this behavior; however, these can be
exploited to achieve the same result as a regular \ehi.

Total \texttt{x-check} headers and unique \texttt{x-check} headers
found in \texttt{nuser} \emails. We found a total of \ehinuserxcheck
\emails in the \texttt{nuser} account. Out of these,
\ehiuniquenuserxcheck had unique form ids that were \emph{not} already
found in the \texttt{maluser} account. We attribute these \emails to
(probably) being sent by a web application that was built with Python
or another language having a similar behavior with respect to ignoring
duplicate headers while constructing an \email, thus appending the
\texttt{x-check} header and \emph{not} the \texttt{bcc} header.
      % Adam: What is the actual behavior? This is confusing. - Changed. DONE.

Total successful injections. This represents the total number of
successful injections. This includes the \ehi with \texttt{bcc}
header\,(1), \texttt{To} header injections\,(3), and Unique
\texttt{x-check} headers found in \texttt{nuser} \emails\,(7). A total
of \success vulnerabilities were found by our system.

### 2016-10-24 Results/disclosure.tex
finally at 13 pages
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

\subsection{Responsible Disclosure of Discovered Vulnerabilities}
After we discovered an \ehi vulnerability on a particular website, we attempted to notify the developers of the vulnerable web application, along with a brief description of the vulnerability.
We chose to \email the following mailboxes, following the rules specified in RFC~2142~\cite{rfc2142}:
\begin{itemize}
	\item \texttt{security@domain.com} - Security bulletins or queries.
	\item \texttt{admin@domain.com} - The administrator of a website.
	\item \texttt{webmaster@domain.com} - Synonym for administrator, same functionality as admin.
\end{itemize}

Out of the \domains\ vulnerable domains found, only \emailedDefaultmailbox websites had the mailboxes able to receive \emails. For the remaining domains, we used the \texttt{whois}~\cite{whois} data to find the contact details of the owner and then \emailed them. The number of emails we sent and the number of developer responses we received is shown in Table~\ref{tab:devresp}.

\begin{table}[tbp]
\centering
\normalsize
\begin{tabular}{|c|c|c|}
	\hline
	\multicolumn{1}{|p{2cm}}{\centering \textbf{Notified websites}} &
	\multicolumn{1}{|p{2cm}|}{\centering \textbf{Developer Responses}} &
	\multicolumn{1}{p{2cm}|}{\centering \textbf{Confirmed discoveries}}\\
	\hline
	\domains\ & \responses & \confirmed \\
	\hline
\end{tabular}
	\caption[\titlecap{}]{Responsible disclosure of the discovered vulnerabilities to developers and the number of received responses.}
	\label{tab:devresp}
\end{table}

% Adam: did we get updated notifications? - updated. DONE.
We received \responses developer responses, confirming \confirmed discovered vulnerabilities. Four of the developers fixed the vulnerability on their website.
% is this done? 1 additional email asking for more information, but no confirmation.
From our research, it is clear that \ehi is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on. This value acts as a \emph{lower bound} for prevalence of \ehi vulnerability, and can quite easily be larger if the attacks were broader, crafted for the individual web application, and  less automated.

>>>>

\subsection{Responsible Disclosure of Discovered Vulnerabilities}
After we discovered an \ehi vulnerability on a particular website, we attempted to notify the developers of the vulnerable web application, along with a brief description of the vulnerability.
We chose to \email the following mailboxes, following the rules
specified in RFC~2142~\cite{rfc2142}: \texttt{security@domain.com},
\texttt{admin@domain.com}, and \texttt{webmaster@domain.com}

Out of the \domains\ vulnerable domains found, only
\emailedDefaultmailbox websites had the mailboxes able to receive
\emails. For the remaining domains, we used the
\texttt{whois}~\cite{whois} data to find the contact details of the
owner and then \emailed them. We received \responses developer
responses, confirming \confirmed discovered vulnerabilities. Four of
the developers fixed the vulnerability on their website.
% is this done? 1 additional email asking for more information, 1 confirmation that i forwarded to you.
From our research, it is clear that \ehi is quite widespread as a
vulnerability, appearing on \successDelta\ of forms that we were able
to perform automated attacks on. This value acts as a \emph{lower
  bound} for prevalence of \ehi vulnerability, and can quite easily be
larger if the attacks were broader, crafted for the individual web
application, and less automated.

%% \begin{table}[tbp]
%% \centering
%% \scriptsize
%% \begin{tabular}{|c|c|c|}
%% 	\hline
%% 	\multicolumn{1}{|p{2cm}}{\centering \textbf{Notified websites}} &
%% 	\multicolumn{1}{|p{2cm}|}{\centering \textbf{Developer Responses}} &
%% 	\multicolumn{1}{p{2cm}|}{\centering \textbf{Confirmed discoveries}}\\
%% 	\hline
%% 	\domains\ & \responses & \confirmed \\
%% 	\hline
%% \end{tabular}
%% 	\caption[\titlecap{}]{Responsible disclosure of the discovered vulnerabilities to developers and the number of received responses.}
%% 	\label{tab:devresp}
%% \end{table}

% Adam: did we get updated notifications? - updated. DONE.

### 2016-10-24 Results/fuzz_result.tex
fixed todos in evaluation
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

\subsection{Fuzzed Data}
Table~\ref{tab:fuzzed_data} shows the quantity of \emails that we received for the benign and malicious payloads. 
\input{Results/fuzzed_data}
\paragraph{\Email received from forms}
The \emails that we received can be categorized into two categories:
\begin{enumerate}
	\item \Emails due to regular payload\\
	This represents the total number of web applications that sent \emails to us. This indicates that we were able to successfully submit the forms on these sites to trigger the web application to send an \email.

	\item \Emails due to malicious payload\\
    Once we receive an \email from a web application due to the regular payload, we fuzz those forms with the malicious payloads. This field represents the total number of unique URLs that are  contain an \ehi vulnerability.
\end{enumerate}

>>>>

%\subsection{Fuzzed Data and Received \Emails}

Table~\ref{tab:fuzzed_data} shows the quantity of \emails that we received for the benign and malicious payloads. 
\input{Results/fuzzed_data}

\noindent\textbf{\Email received from forms.} The \emails that we
received can be categorized into two categories. (1) \Emails due to
regular payload: This represents the total number of web applications
that sent \emails to us. This indicates that we were able to
successfully submit the forms on these sites to trigger the web
application to send an \email. (2) \Emails due to malicious payload:
Once we receive an \email from a web application due to the regular
payload, we fuzz those forms with the malicious payloads. This field
represents the total number of unique URLs that are contain an \ehi
vulnerability.
